Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-27 tensor/draft/draft-tensor-op.tex
[draft] Remove references to polar coordinates and absolute values

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  credibility level
  & 68\%, 95\%
  & 68\%, 95\%
  & 68\%, 95\%
  \\
  \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$, $[-0.52,\, 0.35]$ $\quad$
  & $\quad$ $[-0.29,\, 0.09]$, $[-0.43,\, 0.27]$ $\quad$
  & $\quad$ $[-0.23,\, 0.14]$, $[-0.39,\, 0.30]$ $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
  & $[-0.19,\, 0.21]$, $[-0.37,\, 0.35]$
  & $[-0.17,\, 0.22]$, $[-0.33,\, 0.37]$
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
  & $[-0.19,\, 0.17]$, $[-0.33,\, 0.33]$
  & $[-0.18,\, 0.16]$, $[-0.32,\, 0.32]$
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$, $[-0.44,\, 0.45]$
  & $[-0.21,\, 0.19]$, $[-0.37,\, 0.35]$
  & $[-0.20,\, 0.18]$, $[-0.36,\, 0.35]$
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$, $[0.03,\, 0.57]$
  & $[0.09,\, 0.33]$, $[0.02,\, 0.44]$
  & $[0.10,\, 0.33]$, $[0.02,\, 0.43]$
  \\
  \hline
  \end{tabular}

@@

A keen observer may notice that in \reftab{tab:cTT5:1-dimCLs} the SM point
$\wilson{T,T5} \equiv 0$ is contained in every 68\% region in Cartesian
coordinates but never in even the 95\% region in polar coordinates\footnote{But
  the bin with lower edge $\wilson{T,T5} = 0$ is always in the 99\%
  region.}. This is a consequence of the general \emph{concentration of
  measure}. Another way to look at it is to transform the uniform prior density
from Cartesian to polar coordinates. For the example of a single Wilson
coefficient, say $\wilson{T}$, the transformed density is proportional to the
determinant of the Jacobian which is $|\wilson{T}|$. Since the Cartesian prior
boundaries are much larger than the regions of high likelihood, one could think
the value of the boundary is irrelevant, but in fact it determines the peak of
the prior in polar coordinates. In other words, the uniform prior on
$\mbox{Re}(\wilson{T})$ and $\mbox{Im}(\wilson{T})$ favors larger values of
$|\wilson{T}|$ even though we consider it consensus in the community that
smaller rather than larger values are reasonable because $\wilson{T} = 0$ in the
SM. We suggest therefore that the default treatment be revised in the future to
include available prior knowledge.

@@

Interference terms of $\wilson{P,\,P'}$ with vector couplings might weaken these
bounds. For $\overline{\cal B}(B_s \to \bar\mu\mu)$, the relevant term is
$(\wilson{10} - \wilson{10'})$ (see \refeq{eq:Br-Bsmumu:time0}) and for
$F_H^\ell$ it is $(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw}; both are
suppressed by the factors $m_\mu/M_{B_s}$ and $m_\mu/\sqrt{q^2}$,
respectively. Nevertheless, these terms become important for small
$\wilson{P,\,P'}$ due to the large SM value of $\wilson[SM]{10} \simeq -4.2$. We
compile bounds on complex-valued scalar couplings in \reftab{tab:cSP:1-dimCLs}
for only $F_H^\mu$, only $\overline{\cal B}(B_s \to \bar\mu\mu)$, and their
combination with all the other observables in \reftab{tab:observables}. Neither
$F_H^\ell$ nor $\overline{\cal B}(B_s \to \bar\ell\ell)$ alone can bound all
four complex-valued scalar couplings, however their combination is capable to do
so and moreover, the bounds are stable against destructive interference with
vector couplings. In the case of $\wilson[NP]{9,9',10,10'} \ne 0$, we find the
following bounds with 68\% (95\%) probability:
\begin{equation}
  \label{eq:SP-bounds}
  \begin{aligned}
    \left| \wilson{S} \right| & \in [0.06,\, 0.25]\; ([0.01,\, 0.36]),\\
    \left| \wilson{S'} \right| & \in [0.09,\, 0.46]\; ([0.02,\, 0.73]),\\
    \left| \wilson{P} \right| & \in [0.05,\, 0.21]\; ([0.01,\, 0.32]),\\
    \left| \wilson{P'} \right| & \in [0.11,\, 0.42]\; ([0.02,\, 0.63]).
  \end{aligned}
\end{equation}
Allowing in addition $\wilson{T,T5} \ne 0$, the intervals of
\refeq{eq:SP-bounds} are quite similar but in general (10--20)\% narrower and
shifted by that amount towards zero. Again, this can be explained by the
cumulative effect of $\wilson{S,S',P,P'}$ and $\wilson{T,T5}$ in $F_H^\ell$
shown in \refeq{eq:FH-dependence}.

@@

The most general fit of complex-valued tensor and scalar couplings
$\wilson{S,S',P,P',T,T5}$ in combination with vector couplings
$\wilson{9,\,9',\,10,\, 10'}$---the combination of \refsec{sec:tensor} and
\refsec{sec:scalar}---yields bounds very similar to those in tables
\ref{tab:cTT5:1-dimCLs} and~\ref{tab:cSP:1-dimCLs}. The changes are only small
and in fact the bounds tend to be even more stringent because tensor and scalar
couplings can contribute to $F_H^{\mu}$ only constructively---see
\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of $B\to
K^{*}\bar\mu\mu$ help to improve the constraints on $\wilson{T,\, T5}$. This
demonstrates that even in the case of complex-valued couplings there is enough
information in the data to bound all 20 real and imaginary parts.

@@

In a Bayesian analysis of the complex-valued couplings of the effective theory,
we find that the measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
\item imposes by itself {constraints} on tensor couplings
  $|\wilson{T,\,T5}|$ such that the upper bound of the smallest 68\%
  (95\%) credibility interval is $0.43\, (0.57)$, superseding previous
  bounds.  In combination with current data from $B\to K^* \bar\mu\mu$
  and lattice {predictions of} $B\to K^*$ form factors, the
  bounds are lowered to 0.33 (0.43), even in the presence of
  nonstandard contributions in vector couplings.
  \item for the first time allows to {simultaneously} bound all four scalar couplings
  {$\wilson{S,S',P,P'}$} due to its complementarity to
  $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into account
  destructive interference with vector couplings, $|\wilson{i} + \wilson{i'}| <
  0.3\, (0.6)$ and $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ with
  at least 68\% (95\%) probability. Currently, the bounds from $F_H^\mu$ are
  weaker than those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a
  factor of four. Future measurements of $F_H^\mu$ at LHCb and Belle II will
  further tighten the bounds.

>>>>

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  credibility level
  & 68\%, 95\%
  & 68\%, 95\%
  & 68\%, 95\%
  \\
  \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$, $[-0.52,\, 0.35]$ $\quad$
  & $\quad$ $[-0.29,\, 0.09]$, $[-0.43,\, 0.27]$ $\quad$
  & $\quad$ $[-0.23,\, 0.14]$, $[-0.39,\, 0.30]$ $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
  & $[-0.19,\, 0.21]$, $[-0.37,\, 0.35]$
  & $[-0.17,\, 0.22]$, $[-0.33,\, 0.37]$
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
  & $[-0.19,\, 0.17]$, $[-0.33,\, 0.33]$
  & $[-0.18,\, 0.16]$, $[-0.32,\, 0.32]$
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$, $[-0.44,\, 0.45]$
  & $[-0.21,\, 0.19]$, $[-0.37,\, 0.35]$
  & $[-0.20,\, 0.18]$, $[-0.36,\, 0.35]$
  \\
  \hline
  \end{tabular}

@@

@@

Interference terms of $\wilson{P,\,P'}$ with vector couplings might weaken these
bounds. For $\overline{\cal B}(B_s \to \bar\mu\mu)$, the relevant term is
$(\wilson{10} - \wilson{10'})$ (see \refeq{eq:Br-Bsmumu:time0}) and for
$F_H^\ell$ it is $(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw}; both are
suppressed by the factors $m_\mu/M_{B_s}$ and $m_\mu/\sqrt{q^2}$,
respectively. Nevertheless, these terms become important for small
$\wilson{P,\,P'}$ due to the large SM value of $\wilson[SM]{10} \simeq -4.2$. We
compile bounds on complex-valued scalar couplings in \reftab{tab:cSP:1-dimCLs}
for only $F_H^\mu$, only $\overline{\cal B}(B_s \to \bar\mu\mu)$, and their
combination with all the other observables in \reftab{tab:observables}. Neither
$F_H^\ell$ nor $\overline{\cal B}(B_s \to \bar\ell\ell)$ alone can bound all
four complex-valued scalar couplings, however their combination is capable to do
so and moreover, the bounds are stable against destructive interference with
vector couplings.

@@

The most general fit of complex-valued tensor and scalar couplings
$\wilson{S,S',P,P',T,T5}$ in combination with vector couplings
$\wilson{9,\,9',\,10,\, 10'}$---the combination of \refsec{sec:tensor}
and \refsec{sec:scalar}---yields bounds very similar to those in
tables \ref{tab:cTT5:1-dimCLs} and~\ref{tab:cSP:1-dimCLs}. The changes
are only small and in fact the bounds tend to be even more stringent
\fred{by $\sim (10 - 20) \%$} because tensor and scalar couplings can
contribute to $F_H^{\mu}$ only constructively---see
\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of
$B\to K^{*}\bar\mu\mu$ help to improve the constraints on
$\wilson{T,\, T5}$. This demonstrates that even in the case of
complex-valued couplings there is enough information in the data to
bound all 20 real and imaginary parts.

@@

In a Bayesian analysis of the complex-valued couplings of the effective theory,
we find that the measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
\item imposes by itself {constraints} on \fred{real and imaginary
    parts of the} tensor couplings \fred{$\wilson{T,\,T5}$} such that the
  upper bound of the smallest 68\% (95\%) credibility interval is
  \fred{$ \lesssim 0.25\, (0.45)$}, superseding previous bounds.  In
  combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  {predictions of} $B\to K^*$ form factors, the bounds are lowered to
  \fred{$\lesssim 0.23\, (0.39)$}, even in the presence of nonstandard
  contributions in vector couplings.
\item for the first time allows to {simultaneously} bound all four
  scalar couplings {$\wilson{S,S',P,P'}$} due to its complementarity
  to $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into
  account destructive interference with vector couplings, \fred{all
  credibility intervals contain the SM. The corresponding 1D intervals
  of real and imaginary parts have widths of $\sim 0.6\, (1.2)
  $ for $\wilson{i} + \wilson{i'}$ and $\sim 0.15\, (0.3)$ for
  $\wilson{i} - \wilson{i'}$} for $i = S,P$. Currently, the bounds from
  $F_H^\mu$ are weaker than those from $\overline{\cal B}(B_s \to
  \bar\mu\mu)$ by about a factor of four. Future measurements of
  $F_H^\mu$ at LHCb and Belle II will further tighten the bounds.
